---
title: "DS 3001 Lab 7"
author: "Kate Douglass"
date: "10/13/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(tidytext)
library(ggwordcloud)
library(gutenbergr)
library(textdata)
```

# Reading in Articles - Northeast Region

I copy and pasted articles into a text file.
I have four from the New York Times, two from The Hartford Courant, two from The Keene Sentinental (NH) and two from Bangor Daily News (Maine).
```{r}
northeast<-read_lines("northeast.txt")
```

# Word Frequencies

```{r}
northeast<-tibble(northeast)
northeast<-northeast%>%unnest_tokens(word,northeast)%>%anti_join(stop_words)%>%count(word, sort=TRUE)
```

# Sentiment Analysis

```{r}
northeast_afinn <- northeast %>%
  inner_join(get_sentiments("afinn"))
northeast_nrc <- northeast %>%
  inner_join(get_sentiments("nrc"))
northeast_bing <- northeast %>%
  inner_join(get_sentiments("bing"))

table(northeast_afinn$value)
table(northeast_nrc$sentiment)
table(northeast_bing$sentiment)
```

# Summary

By just looking at the sentiment summaries, we cannot come to the conclusion on if there are more negative words compared to positive. The bing summary tells us there are 186 negatives compared to 106 positives. However, the nrc summary tells us that there are 187 negatives compared to 253 positives. The nrc summary also tell us that there are many words related to trust, fear, and anticipation. However, this is probably the same case in most regions when talking about climate change. We can gather from the afinn summary that there are more negative words than positive ones. This would agree with the bing analysis. Also, by looking at the word frequencies in the northeast articles we can see that they focus a lot on policy, using words such as government, united, city, republican, federal, cost, trump, biden, president. To make more conclusions on the northeast we must look at the sentiment analysis for the other regions of the United States. This is not that surprising due to the northeast being known as more democratic and more focused on politics than other regions of the United States. Also a reason for this could be that the New York Times had four articles included in this analysis, and being a big city newspaper that is widely known, it is more likely to talk about politics and policies.