---
title: "DS 3001 Lab 7"
author: "Kate Douglass"
date: "10/13/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(tidyverse)
library(tidytext)
library(ggwordcloud)
library(gutenbergr)
library(textdata)
```

# Reading in Articles - Northeast Region

I copy and pasted articles into text files.
I have four from the New York Times, two from The Hartford Courant, two from The Keene Sentinental (NH) and two from Bangor Daily News (Maine).
```{r}
a1 <- read_lines("a1.txt")
a2 <- read_lines("a2.txt")
a3 <- read_lines("a3.txt")
a4 <- read_lines("a4.txt")
a5 <- read_lines("a5.txt")
a6 <- read_lines("a6.txt")
a7 <- read_lines("a7.txt")
a8 <- read_lines("a8.txt")
a9 <- read_lines("a9.txt")
a10 <- read_lines("a10.txt")

northeast<-read_lines("northeast.txt")
```

# Word Frequencies

```{r}
#creating a function to find the frequencies of each word in each article
func1 <- function(x){
  x<-tibble(x)
  x<-x %>%
  unnest_tokens(word,x)%>%
  anti_join(stop_words)%>% 
  count(word, sort=TRUE)
}

a1<-func1(a1)
a2<-func1(a2)
a3<-func1(a3)
a4<-func1(a4)
a5<-func1(a5)
a6<-func1(a6)
a7<-func1(a7)
a8<-func1(a8)
a9<-func1(a9)
a10<-func1(a10)
northeast<-func1(northeast)
```


# Sentiment Analysis

```{r, include=FALSE}
get_sentiments('afinn') #several different values
get_sentiments('nrc') #several different categories
get_sentiments('bing') #positive or negative
```

```{r}
a1_afinn <- a1 %>%
  inner_join(get_sentiments("afinn"))
a1_nrc <- a1 %>%
  inner_join(get_sentiments("nrc"))
a1_bing <- a1 %>%
  inner_join(get_sentiments("bing"))

afinnfunc<-function(x){
  x%>%inner_join(get_sentiments("afinn"))
}
nrcfunc<-function(x){
  x%>%inner_join(get_sentiments("nrc"))
}
bingfunc<-function(x){
    x%>%inner_join(get_sentiments("bing"))
}

a2_afinn<-afinnfunc(a2)
a2_nrc<-nrcfunc(a2)
a2_bing<-bingfunc(a2)

a3_afinn<-afinnfunc(a3)
a3_nrc<-nrcfunc(a3)
a3_bing<-bingfunc(a3)

a4_afinn<-afinnfunc(a2)
a4_nrc<-nrcfunc(a2)
a4_bing<-bingfunc(a2)

a5_afinn<-afinnfunc(a2)
a5_nrc<-nrcfunc(a2)
a5_bing<-bingfunc(a2)

a6_afinn<-afinnfunc(a2)
a6_nrc<-nrcfunc(a2)
a6_bing<-bingfunc(a2)

a7_afinn<-afinnfunc(a2)
a7_nrc<-nrcfunc(a2)
a7_bing<-bingfunc(a2)

a8_afinn<-afinnfunc(a2)
a8_nrc<-nrcfunc(a2)
a8_bing<-bingfunc(a2)

a9_afinn<-afinnfunc(a2)
a9_nrc<-nrcfunc(a2)
a9_bing<-bingfunc(a2)

a10_afinn<-afinnfunc(a10)
a10_nrc<-nrcfunc(a10)
a10_bing<-bingfunc(a10)

northeast_afinn<-afinnfunc(northeast)
northeast_nrc<-nrcfunc(northeast)
northeast_bing<-bingfunc(northeast)
```

# Reading in Articles - Northeast Region

I copy and pasted articles into a text file.
I have four from the New York Times, two from The Hartford Courant, two from The Keene Sentinental (NH) and two from Bangor Daily News (Maine).
```{r}
northeast<-read_lines("northeast.txt")
```

# Word Frequencies

```{r}
northeast<-tibble(northeast)
northeast<-northeast%>%unnest_tokens(word,northeast)%>%anti_join(stop_words)%>%count(word, sort=TRUE)
```


# Sentiment Analysis

```{r}
northeast_afinn <- northeast %>%
  inner_join(get_sentiments("afinn"))
northeast_nrc <- northeast %>%
  inner_join(get_sentiments("nrc"))
northeast_bing <- northeast %>%
  inner_join(get_sentiments("bing"))
```

