---
title: "text_lab"
author: "Catherine Schuster"
date: "10/18/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## West
### Analysis:
Similar to the midwest, through word frequency, we see a focused concern over global warming factors most relevant to western climates and geographies. In this case, “fires” and “burning” are two frequently used words in western-published articles, which indicate a general sentiment of panic about the emergence of wildfires in these drier climates. Additionally, a concern with science, fact, and truth is also seen through our analysis, as “Science”, “scientists”, “scientific“, and “hope” were also among the top words quoted in these articles.
70% of the words in these articles and opinion pieces (not including stop  words) were classified as negative under Bing sentiment analysis. This could lead to a generalized conclusion that the West is concerned over climate change and its environmental effects, yet hopeful about what science can contribute.


```{r}
library(tidyverse)
library(tidytext)
library(ggwordcloud)
library(gutenbergr)
library(textdata)
save.image("tidytext.RData")
```

```{r}
west <- read_lines("/Users/catherineschuster/Desktop/Fall 2021/DS 3001/DS-3001-Main/07_text_mining/DS3001-Lab7/West/west.txt")

west <- tibble(west)
View(west)

west$west <- as.character(west$west)

View(west)

west <- west %>%
  unnest_tokens(word, west)%>%
  anti_join(stop_words)%>% 
  count(word, sort=TRUE)

View(west)
```

```{r}
west_sentiment_afinn <- west %>%
  inner_join(get_sentiments("afinn"))
  
west_sentiment_nrc <- west %>%
  inner_join(get_sentiments("nrc"))

west_sentiment_bing <- west %>%
  inner_join(get_sentiments("bing"))


table(west_sentiment_bing$sentiment)
table(west_sentiment_nrc$sentiment)
View(west_sentiment_afinn)
```



